TBD

### 2024-04-08 outputs/paper/paper.qmd
references updated, appendix formated

# read in data
state_house_price_by_year <- read_csv("outputs/data/state_house_price_by_year.csv")
state_house_price_by_month <- read_csv("outputs/data/state_house_price_by_month.csv")

state_1b_house_price_by_year <- read_csv("outputs/data/state_1b_house_price_by_year.csv")
state_2b_house_price_by_year <- read_csv("outputs/data/state_2b_house_price_by_year.csv")
state_3b_house_price_by_year <- read_csv("outputs/data/state_3b_house_price_by_year.csv")
state_4b_house_price_by_year <- read_csv("outputs/data/state_4b_house_price_by_year.csv")
state_5bplus_house_price_by_year <- read_csv("outputs/data/state_5bplus_house_price_by_year.csv")

state_1b_house_price_by_month <- read_csv("outputs/data/state_1b_house_price_by_month.csv")
state_2b_house_price_by_month <- read_csv("outputs/data/state_2b_house_price_by_month.csv")
state_3b_house_price_by_month <- read_csv("outputs/data/state_3b_house_price_by_month.csv")
state_4b_house_price_by_month <- read_csv("outputs/data/state_4b_house_price_by_month.csv")
state_5bplus_house_price_by_month <- read_csv("outputs/data/state_5bplus_house_price_by_month.csv")

@@

Data used in this paper was cleaned, processed and tested with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `readr` [@citeReadr], `knitr` [@citeKnitr], `rstanarm` [@citeRstanarm], `modelsummary` [@citeModelsummary], `tidybayes` [@citeTidybayes], `loo` [@citeLoo], `testthat` [@citeTestthat], `KableExtra` [@citeKableEx].

@@

>>>>

# read in data
house_prices <- read_csv("../../outputs/data/merged_house_price.csv")

state_house_price_by_year <- read_csv("../../outputs/data/state_house_price_by_year.csv")
state_1b_house_price_by_year <- read_csv("../../outputs/data/state_1b_house_price_by_year.csv")
state_2b_house_price_by_year <- read_csv("../../outputs/data/state_2b_house_price_by_year.csv")
state_3b_house_price_by_year <- read_csv("../../outputs/data/state_3b_house_price_by_year.csv")
state_4b_house_price_by_year <- read_csv("../../outputs/data/state_4b_house_price_by_year.csv")
state_5bplus_house_price_by_year <- read_csv("../../outputs/data/state_5bplus_house_price_by_year.csv")

state_house_price_by_month <- read_csv("../../outputs/data/state_house_price_by_month.csv")
state_1b_house_price_by_month <- read_csv("../../outputs/data/state_1b_house_price_by_month.csv")
state_2b_house_price_by_month <- read_csv("../../outputs/data/state_2b_house_price_by_month.csv")
state_3b_house_price_by_month <- read_csv("../../outputs/data/state_3b_house_price_by_month.csv")
state_4b_house_price_by_month <- read_csv("../../outputs/data/state_4b_house_price_by_month.csv")
state_5bplus_house_price_by_month <- read_csv("../../outputs/data/state_5bplus_house_price_by_month.csv")

@@

Data used in this paper was cleaned, processed and tested with the programming language R [@citeR]. Also with support of additional packages in R: `tidyverse` [@citeTidyverse], `ggplot2` [@citeGgplot], `janitor` [@citeJanitor], `readr` [@citeReadr], `knitr` [@citeKnitr], `modelsummary` [@citeModelsummary], `testthat` [@citeTestthat], `KableExtra` [@citeKableEx], `viridis` [@citeViridis], `lubridate` [@citeLubridate], `maps` [@citeMaps], `mgcv` [@citeMgcv].

@@

\appendix

# Appendix

## Datasheet

**Motivation**

**Composition**

**Collection process**

**Preprocessing/cleaning/labeling**

**Uses**

**Distribution**

**Maintenance**
